\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
Moved paragraph on wristband to biometric tools

@@

%In a nutshell, the use of gaze data as an assessment of the human-robot
%interaction in an educational setting provides future research
%prospects. The data acquisition is a better trade-off between the
%ecological validity of the experiment (as there cannot be an interaction
%with the robot fMRI data acquisition) and the precision of the data
%stream (wristbands for measuring the palpitation and the temperature).

>>>>

In a nutshell, the use of gaze data as an assessment of the human-robot
interaction in an educational setting provides future research
prospects. The data acquisition is a better trade-off between the
ecological validity of the experiment (as there cannot be an interaction
with the robot fMRI data acquisition) and the precision of the data
stream (wristbands for measuring the palpitation and the temperature).

@@
